\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-29 paper/RDF validation requirements/RDF validation requirements.tex
evaluation

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0cm}
	\begin{center}
	\textbf{\vspace{0.4cm}Mapping to RDF-CO:} \\
  \begin{tabular}{l|l|l|l|l|l|l}
	\hline
  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
  \hline

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & $\sqsubseteq$ \\
\end{gcotable}

@@

@@

@@

\section{Vocabulary}
Vocabularies should not invent any new terms or use deprecated elements.

@@

@@

\begin{evaluation-generic-overview}
Property Constraints & 48 & 65 (64.86) \\
Class Constraints & 17 & 23 (22.96) \\
Property and Class Constraints & 9 & 12 (12.16) \\
\hline
Simple Constraints & 46 & 62 (62.16) \\
Simple Constraints (Syntactic Sugar) & 10 & 14 (13.51) \\
Complex Constraints & 18 & 24 (24.32) \\
\hline
DL Expressible & 51 & 69 (68.92) \\
DL Not Expressible & 23 & 31 (31.08) \\
\hline
Total & 74 & 100 \\
\end{evaluation-generic-overview}

@@

\begin{evaluation-generic}
Context-Specific Valid Classes & \ding{55} & $\checkmark$ & \ding{55} \\   
Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Default Values & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Matching & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Whitespace Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
HTML Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Conditional Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Recommended Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Handle RDF Collections & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Value is Valid for Datatype & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Use Sub-Super Relations in Validation & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Class-Specific Irreflexive Object Properties & & & \\
Provenance & & & \\
Data Model Consistency & & & \\
Structure & & & \\  
Labeling and Documentation & & & \\
Vocabulary & & & \\
HTTP URI Scheme Violation & & & \\
\end{evaluation-generic}

>>>>

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0cm}
	\begin{center}
	\textbf{\vspace{0.4cm}Mapping to RDF-CO:} \\
  \begin{tabular}{l|l|l|l|l|l|l}
	\hline
  \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
  \hline

@@

\begin{gcotable}
property & $\exists$ marriedTo . Self & knows & - & Self & $\exists$ \\
class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ \\
\end{gcotable}

@@

\emph{Persons} cannot be married to themselves.

\begin{DL}
Person $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$ 
\end{DL}

\begin{gcotable}
property & $\exists$ marriedTo . Self & knows & - & Self & $\exists$ \\
class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ knows . Self & $\neg$ \\
class & Person & - & - & Person, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ \\
\end{gcotable}

\begin{gcotable}
property & Person & marriedTo & - & - & irreflexive \\
\end{gcotable}

@@

Any provenance information must be available for instances of given classes.

For \emph{publications}, any provenance information must be available.

\begin{gcotable}
class & Publication & - & - & - & provenance & - \\
\end{gcotable}

@@

\section{Vocabulary}

Vocabularies should not invent any new terms or use deprecated elements.

\begin{gcotable}
class & $\top$ & - & - & - & vocabulary & - \\
\end{gcotable}

@@

\begin{gcotable}
class & $\top$ & - & - & - & HTTP URI Scheme Violation & - \\
\end{gcotable}

@@

\begin{evaluation-generic-overview}
Property Constraints & 49 & 60 (60.49) \\
Class Constraints & 20 & 25 (24.96) \\
Property and Class Constraints & 12 & 15 (14.81) \\
\hline
Simple Constraints & 49 & 60 (60.49) \\
Simple Constraints (Syntactic Sugar) & 11 & 14 (13.58) \\
Complex Constraints & 21 & 26 (25.93) \\
\hline
DL Expressible & 52 & 64 (64.2) \\
DL Not Expressible & 29 & 36 (35.80) \\
\hline
Total & 81 & 100 \\
\end{evaluation-generic-overview}

@@

\begin{evaluation-generic}
Context-Specific Valid Classes & \ding{55} & $\checkmark$ & \ding{55} \\   
Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Default Values & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Matching & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Language Tag Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Whitespace Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
HTML Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Conditional Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Recommended Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Handle RDF Collections & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Value is Valid for Datatype & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
Use Sub-Super Relations in Validation & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\

*Class-Specific Irreflexive Object Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\
Provenance & \ding{55} & $\checkmark$ & \ding{55} \\
Data Model Consistency & $\sim$ & \ding{55} & \ding{55} \\
Structure & $\sim$ & \ding{55} & \ding{55} \\ 
Labeling and Documentation & $\sim$ & \ding{55} & \ding{55} \\
Vocabulary & \ding{55} & $\checkmark$ & \ding{55} \\
HTTP URI Scheme Violation & \ding{55} & $\checkmark$ & \ding{55} \\
\end{evaluation-generic}

### 2015-05-29 paper/paper 2/dc-2015.tex
evaluation

When language designers extend constraint languages 
to be able to formulate constraints of not yet supported constraint types,
our proposal prevents the necessity to actually implement the validation of data
according to constraints of these constraint types for each of those languages.  
For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
%validation implementations out-of-the-box for any constraint type whose \emph{specific constraints} may be expressed by any language  
by providing a \emph{SPIN} mapping
%generic validation implementations once 
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}  
whose constraints are represented generically \cite{BoschEckert2015-2}.
%(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
\textcolor{red}{19} of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
This means that for these \textcolor{red}{19} constraint types there must be \textcolor{red}{76} implementations (four for each constraint type) to actually validate RDF data according to \textcolor{red}{76} \emph{specific constraints} - instead of only \textcolor{red}{19} implementations (one for each \emph{generic constraint}). 
%which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
leads to exactly the same validation results, 
i.e., that validation is performed independently from the used language.
This is not the case, however, for existing languages due to differences in semantics and since they are implemented independently form each other.

@@

We classify sets of constraints according to four dimensions.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in which set of constraints their instances are contained.
%In the following, we state the rounded number of associated constraint types in brackets.
%\begin{itemize}
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%\end{itemize}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
As we express constraints of each constraint type in form of \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015},
we show that constraints of any constraint type can be described generically.
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 70\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (30\%). 
%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (2/3 of the constraint types) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
%In case \emph{complex constraints} are expressible in \emph{DL}, 
%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
Constraints of almost 15\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
on classes (\emph{class constraints}, 1/5), or
on properties and classes (\emph{property and class constraints}, 1/10).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.

There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
Thus, the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
Constraints can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)} or specifically (\emph{specific constraint}) by domain-specific constraint languages.
Hence, we mapped constraint types to \emph{DL} 
in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation \ref{sec:vocabulary}).

@@

It is part of future work 
(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using \emph{generic constraints} as intermediate representation.

>>>>

When language designers extend constraint languages 
to be able to formulate constraints of not yet supported constraint types,
our proposal prevents the necessity to actually implement the validation of data
according to constraints of these constraint types for each of those languages.  
For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
%validation implementations out-of-the-box for any constraint type whose \emph{specific constraints} may be expressed by any language  
by providing a \emph{SPIN} mapping
%generic validation implementations once 
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}  
whose constraints are represented generically \cite{BoschEckert2015-2}.
%(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
19 of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
This means that for these 19 constraint types there must be 76 implementations (four for each constraint type) to actually validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}). 
%which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
leads to exactly the same validation results, 
i.e., that validation is performed independently from the used language.
This is not the case, however, for existing languages due to differences in semantics and since they are implemented independently form each other.

@@

We classify sets of constraints according to four dimensions.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in which set of constraints their instances are contained.
%In the following, we state the rounded number of associated constraint types in brackets.
%\begin{itemize}
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%\end{itemize}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
As we express constraints of each constraint type in form of \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015},
we show that constraints of any constraint type can be described generically.
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 64\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (36\%). 
%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (60\% of the constraint types) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (26\%) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
%In case \emph{complex constraints} are expressible in \emph{DL}, 
%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
Constraints of almost 14\% of the constraint types are \emph{complex constraints}
which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 60\%),
on classes (\emph{class constraints}, 25\%), or
on properties and classes (\emph{property and class constraints}, 15\%).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

%Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group, 
%we published by today 81 constraint types \cite{BoschNolleAcarEckert2015}
%which form the basis to
%lay the ground for discussions on validation
%by defining a basic terminology and classification system for RDF constraints.

Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we published by today 81 requirements to validate RDF data and to formulate constraints; 
each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
These constraint types form the basis to
lay the ground for discussions on validation
by defining a basic terminology and classification system for RDF constraints.
%
There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
Thus, the idea behind this paper is to satisfy all requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
%we mapped constraint types to \emph{DL} 
%to determine which \emph{DL} constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).

@@

It is part of future work 
(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using the developed vocabulary to intermediately represent constraints.
Identifying RDF validation requirements is an ongoing process,
so the task to map constraints of new constraint types to the vocabulary.
